### 2021-09-21 sections/introduction.tex
modify introduction

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels. More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
data-driven fake estimations from QCD multi-jet background.

>>>>

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
decay of $W$ boson hadronically and leptonically from the $t\rightarrow Wb$ decay, referred as $t_h$ and $t_l$ respectively. The $H\rightarrow \tau\tau$ decay detected to be in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channel. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channel. More regions are exploited compared to the FCNC $\Htautau$ search conducted using early Run~2 data amounting to 36fb$^{-1}$.
The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
data-driven fake estimations from QCD multi-jet background.
